%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Julius-Maximilian-University Würzburg} % Institution
    {MSc in Computer Science - Specialization in Artificial Intelligence} % Degree
    {Grade 1.5} % Location
    {Apr. 2021 - Sep. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Focused on data processing and machine learning, specialized in the field of computer vision.}
        \item {Thesis topic: Real-Time Rendering Super Resolution with Unreal Engine 5}
        \item {Notable Courses: Computational geometry, Machine learning for NLP, Programming with neural nets}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Julius-Maximilian-University Würzburg} % Institution
    {BSc in Games Engineering} % Degree
    {Grade 1.8} % Location
    {Oct. 2017 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Focused on of math, algorithms/datastructures and programming for real-time interactive systems.}
        \item {Thesis topic: Crowdsourced Help Facility Design and Management for Authoring Platforms}
        \item {Notable Courses: Algorithms and datastructures, Software technology, Logic for informatics}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Friedrich Alexander University Erlangen} % Institution
{Physics studies} % Degree
{No degree} % Location
{Oct. 2013 - Mar. 2017} % Date(s)
{}

%---------------------------------------------------------
\cventry
{Werner-von-Siemens-Gymnasium Weißenburg i. Bay.} % Institution
{Allgemeine Hoschulreife - Abitur} % Degree
{Grade 2.7} % Location
{Sep. 2005 - Jul. 2013} % Date(s)
{}

%---------------------------------------------------------
\end{cventries}
