%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Julius-Maximilian-University} % Organization
    {Research Assistant - C\# Developer} % Job title
    {Würzburg, Bayern} % Location
    {Nov. 2021 - Sep. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked part-time on a de-serializer for 3D scene data (json) to import scenes from the Mozilla Spoke editor into the Unity editor.}
        \item {Ensured that the behavior of the scene objects is mimicked correctly, e.g. lights in the scene influence other objects correctly.}
        \item {Encapsulated this functionality in modules (implemented in C\#) to remove the dependency once the scene is converted.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Julius-Maximilian-University} % Organization
    {Teaching Assistant - C++ Developer} % Job title
    {Würzburg, Bayern} % Location
    {Aug. 2021 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught part-time a course about building real-time interactive systems (used as game engines) in C++ while using CMake.}
        \item {Illustrated by a small 2D space shooter game, handling rendering (OpenGL), input (GLFW), 3D models (GLTF), physics (Box2D), audio (SoLoud) and GUI (Dear ImGui).}
        \item {Re-/worked on an existing C++ code base, hosted on Gitlab, and maintaining the documentation (Markdown).}
        \item {Supervised students on their own code projects.}
      \end{cvitems}
    }
  
  %---------------------------------------------------------
  \cventry
    {Gentle Troll Entertainment GmbH} % Organization
    {Internship - C\# Developer} % Job title
    {Würzburg, Bayern} % Location
    {Mar. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programmed game play logic in C\# for a serious game teaching children about sport management developed with Unity.}
        \item {Worked together with the team in a agile Scrum environment.}
      \end{cvitems}
    }

% %---------------------------------------------------------

\end{cventries}
