%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
% \colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
\definecolor{awesome}{HTML}{e92329}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Tobias}{Brandner}
\position{MSc Computer Science{\enskip\cdotp\enskip}Specialization in Artificial Intelligence}
\address{Semmelstraße 9, 97070 Würzburg, Bavaria - Germany}

\mobile{(+49) 179 829 8854}
\email{tobias.brandner@gmx.de}
\homepage{brandnerkasper.github.io}
\github{BrandnerKasper}
\linkedin{tobias-brandner}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``There is a difference between forgetting something and never having learned it." - Dr. Frederic P. Schuller}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Prof. Dr. Alexander Hann}
  {University Hospital Würzburg Medical Clinic and Polyclinic II (ZIM)\\ Oberdürrbacher Str. 6, 97080 Germany}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application - Game Developer for immersive medical VR applications}
% How the letter is opened
\letteropening{Dear Prof. Dr. Alexander Hann,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Tobias Brandner~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  I appreciated our conversation on \textbf{February 13 at 10:30 AM} regarding the \textbf{Game Developer} position at the University Hospital 
  Würzburg. The prospect of contributing to immersive \textbf{medical VR applications} that enhance medical training, 
  reduce reliance on animal testing, and ultimately improve patient care resonates with me.

  I hold a \textbf{Master’s degree in Computer Science with a specialization in Artificial Intelligence} and a 
  \textbf{Bachelor’s degree in Games Engineering} from the \textbf{University of Würzburg}. 
  My background uniquely positions me at the intersection of \textbf{game development, artificial intelligence, and real-time interactive systems}, 
  aligning well with the objectives of your team.
  
  During my academic and professional journey, I have been actively involved in \textbf{VR and game development projects}, including:
  
  \begin{itemize}
      \item \textbf{VIA-VR (Medical VR Research Project):} 
      Developed the backend for a \textbf{Unity-based VR platform} that allows doctors to create customized VR training applications 
      for scenarios like \textbf{first aid training and exposure therapy}. 
      My primary contributions included implementing scene deserialization, ensuring correctness of game objects 
      and integrating assets.
      \item \textbf{Abyssal Enigma (VR Game, Unreal Engine 5):} 
      Designed and implemented a \textbf{first-person underwater exploration game} in a team of 6, 
      handling both \textbf{VR porting and motion sickness reduction techniques} (e.g., virtual nose and FOV adjustments). 
      This experience provided me with a deep understanding of player comfort in VR.
  \end{itemize}
  
  Having worked with both \textbf{Unreal Engine and Unity},
  I am proficient in \textbf{C++, C\#, and Python}. 
  My expertise spans \textbf{real-time systems programming, AI integration, and performance optimization for VR applications}. 
  Additionally, I am skilled in \textbf{3D modeling, animation, and asset integration} using \textbf{Blender}, 
  enabling me to contribute to both technical and artistic aspects of development.
  
  Beyond technical expertise, 
  I thrive in \textbf{team-oriented and research-driven environments}. 
  As a teaching assistant in \textbf{game engine development}, 
  I mentored students on real-time rendering and advanced design patterns to handle complex code bases, 
  reinforcing my ability to \textbf{collaborate, explain complex topics, and document processes clearly}. 
  My research in \textbf{game flow design for 3D platformers}, presented at the IEEE Conference of Games in Milan, 
  demonstrates my ability to 
  \textbf{analyze interactive experiences, conduct structured investigations, and contribute innovative ideas to game development 
  and user experience design}.
  
  I am particularly excited about the potential of \textbf{VR in medical training}
  —leveraging immersive simulations to provide \textbf{realistic, hands-on learning environments for medical professionals}. 
  The ability to replicate complex procedures in a risk-free environment aligns with my passion for using 
  \textbf{game technology to solve real-world problems}. 
  My experience with \textbf{VIA-VR} has already introduced me to the challenges of 
  \textbf{designing medical training simulations}, and I am eager to expand this work in a setting that directly impacts the day to day effort of doctors.
  
  I would love the opportunity to discuss in more detail how my experience and skills can contribute to your research and development efforts. 
  I look forward to your response and hope to speak with you again soon.
  
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
