%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{CV - Tobias Brandner} % Your name
\address{Semmelstraße 9, 97070 Würzburg} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+49)-179-829-8854 \\ tobias.brandner@gmx.de} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
%--copy and paste this region  if you need more--
{\bf MSc in Computer Science - Specialization in Artificial Intelligence} \hfill {Grade \bf1.5} 
\\ Julius-Maximilian-University Würzburg \hfill {\em April 2021 - September 2024}
\\ {\small {\bf Thesis topic:} Real-time rendering super resolution with Unreal Engine 5}
\\ {\small {\em Notable courses:} Computational geometry, Machine learning for NLP, Programming with neural nets} 

{\small
{\bf BSc in Games Engineering} \hfill {Grade \bf 1.8} 
\\ Julius-Maximilian-University Würzburg \hfill {\em October 2017 - September 2021}
}
\\ {\small {\bf Thesis topic:} Crowdsourced Help Facility Design and Management for Authoring Platforms}
%--copy and paste this region  if you need more--

{\small
{\bf Physics Studies} \hfill {No degree} 
\\ Friedrich-Alexander-University Erlangen \hfill {\em October 2013 - March 2017}
}

{\small
{\bf Abitur} \hfill {Grade \bf 2.7} 
\\ Werner-von-Siemens-Gymnasium Weißenburg/Bay. \hfill {\em September 2005 - July 2013}
}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
%--copy and paste this region  if you need more--
{\small
{\bf C\# Developer (Research project)}{, Julius-Maximilian-University} \hfill {\em November 2021 - August 2023}\\
{\small {\em Technologies:} C\#, Unity} 
\begin{itemize}
    \item \small Transformed 3D scene data from Mozilla Spoke to Unity, ensuring functional replication.
\end{itemize}
}
%--copy and paste this region  if you need more--
{\small
{\bf C++ Developer (Teaching Role)}{, Julius-Maximilian-University} \hfill {\em August 2021 - August 2023}\\
{\small {\em Technologies:} C++, OpenGL, CMake}
\begin{itemize}
    \item \small Taught a course about game engine development, designed C++ examples and documented concepts.
\end{itemize}
}
%--copy and paste this region  if you need more--
{\small
{\bf Software Developer (Internship)}{, Gentle Troll Entertainment GmbH} \hfill {\em March 2021 - June 2021}\\
{\small {\em Technologies:} C\#, Unity}
\begin{itemize}
    \item \small Programmed game play logic for a serious game about sport management in Unity.
\end{itemize}
}
\end{rSection}

%--------------------------------------------------------------------------------
%    PROJECTS
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
%--copy and paste this region  if you need more--
{\small
{\bf Real-Time Rendering Super Resolution with Unreal Engine 5} \hfill {\href{https://github.com/BrandnerKasper/URTSR}{Github}} \\
{\small {\em Technologies:} Python, Pytorch, Unreal Engine 5}
\begin{itemize}
    \item \small Developed a neural method to increase resolution and quality of rendered content in real-time.
\end{itemize}
}
% Gaming focus
{\small
{\bf Abyssal Enigma - Dive In Edition (VR)} \hfill {\href{https://miggli.itch.io/abyssal-enigma/devlog/638746/abyssal-engima-dive-in-edition-vr}{Itchio}} \\
{\small {\em Technologies:} Unreal Engine 5, VR, Blender}
\begin{itemize}
   \item \small Designed and developed a first person character for a deep sea exploration game and ported it to VR.
\end{itemize}
}

% AI
%--copy and paste this region  if you need more--
{\small
{\bf Multi Language Image Classification} \hfill {\href{https://github.com/BrandnerKasper/MP_CustomCoOp}{Github}} \\
{\small {\em Technologies:} Python, Pytorch, Jupiter Notebook}
\begin{itemize}
    \item \small Modified context based methods for vision and language classification to work in a multi-lingual context.
\end{itemize}
}

{\bf Boss'n Run - Exploring Game Flow} \hfill {\href{https://brandnerkasper.itch.io/bossn-run}{Itchio}} \\
{\small {\em Technologies:} Python, Unreal Engine 5, C++, Blender}
\begin{itemize}
   \item \small Implemented and analyzed different movement mechanics for 3D jump'n runs.
\end{itemize}

% C++

{\bf Eternal Game Engine} \hfill {\href{https://github.com/BrandnerKasper/Eternal}{Github}} \\
{\small {\em Technologies:} C++, OpenGL, PreMake}
\begin{itemize}
   \item \small Developed a game engine with OpenGL as render backend and an editor written with Dear ImGui.
\end{itemize}


%--copy and paste this region  if you need more--
\end{rSection}

%--------------------------------------------------------------------------------
%    Publications
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Publications}
%--copy and paste this region  if you need more--
{\small
{\bf Analysis and Generation of Flow in 3D Jump’n’Run Games.} \hfill {\href{https://ieeexplore.ieee.org/abstract/document/10645536}{PDF}}\\
\small 2024 IEEE Conference on Games (CoG). Tobias Brandner, Marc Mußmann, and Sebastian von Mammen.\\
}
{\bf Investigating Crowdsourced Help Facilities for Enhancing User Guidance.} \hfill {\href{https://diglib.eg.org/server/api/core/bitstreams/f635ab29-9038-4e8f-8563-89c7def8902f/content}{PDF}}\\
2023 IMET. \\
Sooraj Babu, Tobias Brandner, Samuel Truman, Sebastian von Mammen. \\\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
    \begin{tabular}{>{\bfseries}l l} % Bold the first column
        \small Languages: & Python, C++, C\#, Java, Rust \\
        \small Frameworks/Libraries: & Pytorch, OpenCV, Matplotlib, Pandas, OpenGL\\%, Unreal, Unity \\
        %\small Network architectures: & CNN, ViT, RNN \\
        % \small Game Engines: &  \\ %, Godot \\
        \small Tools: & Git, CMake, Unreal, Unity, Blender \\
    \end{tabular}
\end{rSection}

\end{document}----------------------------

